\documentclass[10pt]{article}
\usepackage[colorlinks=true,linkcolor=black,urlcolor=black,citecolor=black]%
{hyperref}
\usepackage{proof}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{stmaryrd}

\title{SOFTWARE:\\
Scalable, ad-hOc Frameworks and Toolchains for Writing
Algorithms on commodity hardwaRE}
\author{Carlo Angiuli}
\date{April 1, 2016}

\begin{document}
\maketitle
\begin{abstract}
The explosive growth of problems has led to a pressing need for solutions.
Such problems often require the use of algorithms---sequences of operations
for calculating functions. Although computers are notoriously difficult to use,
in this paper we propose the SOFTWARE method of using computers to run
algorithms.
\end{abstract}

Computers are an important tool for running algorithms in the presence of time
constraints, but programming---the process of implementing an algorithm on a
computer---is notoriously challenging and time-consuming. This is because
programming requires an understanding of both computers and algorithms.

With Moore's law coming to an end, it has become increasingly important that


\begin{itemize}
\item
in the presence of - constraints
\item
Distributed systems are notoriously hard to get right.
\item
Writing low-level concurrent code is well known to be challenging and error prone.
\item
Model-checking is a powerful technique for exhaustively testing code. However,
scaling model checking presents a significant challenge.
\item
Proving that a - is correct is important.
\item
We present an algorithm for -
\item
have some well-known but challenging properties.
\item
proven challenging to implement.
\item
Improving performance is a central concern for software developers.
\item
At present \emph{there is no good way}
\item
Powerful abstractions simplify reasoning about
\item
Unfortunately, - is problematic, for multiple reasons.
\end{itemize}

\end{document}
